How to improve your relationship with your future self.

### 2016-06-24 workflow.Rmd
Added a comment
small change

@@

We have experimented with several systems so far: (1) we wrote this paper in R markdown (Jake) and Atom (Maarten) and organized our files and collaboration on Github. The source code can be accessed, downloaded and modified from <https://github.com/jwbowers/workflow>. The program also allowed us to send notes to each other. The nice thing about github is that is enables you to make "releases" of a project which enable you to smooth the reproduction of all of the
products of your research (simulations, data analyses, tables, figures, etc..). Similar features are offered by the Open Science Framework (https://osf.io/), Maarten recently participated in a workshop on research transparency organized by the Berkeley Institute for Transparency in the Social Sciences (www.bitss.org), all course material was accessible through OSF (https://osf.io/qh2nr/). Both platforms, OSF and Github nicely integrate and a key benefit is that they have been created to remain for a long time (unlike perhaps your university drive); (2) for one paper Jake simply included a Sweave document and data files into a compressed archive [@bowers2005dataverse] [SAY ABIT MORE ABOUT WHAT SWEAVE IS IN PRINCIPLE]; (3) for another more computing intensive paper Jake
assembled a set of files that enabled reproduction of our results using the
`make` system [@bowers2008dataverse] [EXPLAIN A BIT MORE OR INCLUDE REF TO WEBSITE?]; (4) Jake also tried the "compendium"
approach [@gentleman2005reproducible,@gentleman2007statistical] which embeds an
academic paper within the R package system [@bowers2011dataverse]; The benefit of the compendium approach is that one is not required to have
access to a command line for `make`: the compendium is downloadable from within
R using `install.packages()` and is viewable using the `vignette()` function in
any operating system than runs R.^[Notice that Jake's reproduction archives and/or
instructions for using them are hosted on the
[Dataverse](http://thedata.org/book/learn-about-project), which is another
system designed to enhance academic collaboration across time and space.]  The
idea that one ought to be able to install and run and use an academic paper
just as one installs and uses statistical software packages is very attractive,
and we anticipate that it will become ever easier to turn papers into R packages
as creative and energetic folks turn their attention to the question of
reproducible research.^[See for example <http://r-pkgs.had.co.nz/>]
Finally, (5) Maarten has been using Dropbox for most of his collaborative projects (https://www.dropbox.com/). ALREADY ABOVE?

There are some new noteworthy developments also. For example, and similar to R Markdown/KnitR in R Studio, there is Markdoc for STATA users (https://github.com/haghish/MarkDoc). People at UC Berkeley have been developing a is a web app, Jupyter Notebook (http://jupyter.org/), that enables you to make and share documents that include text, code, equations and visualizations in one. For researchers working across difference platforms, there is Docker (https://www.docker.com/).

>>>>

<!-- An example comment -->

@@

We have experimented with several systems so far: (1) we wrote this paper in R markdown (Jake) and Atom (Maarten) and organized our files and collaboration on Github. The source code can be accessed, downloaded and modified from <https://github.com/jwbowers/workflow>. The program also allowed us to send notes to each other. The nice thing about github is that is enables you to make "releases" of a project which enable you to smooth the reproduction of all of the
products of your research (simulations, data analyses, tables, figures, etc..). Similar features are offered by the Open Science Framework (https://osf.io/), Maarten recently participated in a workshop on research transparency organized by the Berkeley Institute for Transparency in the Social Sciences (www.bitss.org), all course material was accessible through OSF (https://osf.io/qh2nr/). Both platforms, OSF and Github nicely integrate and a key benefit is that they have been created to remain for a long time (unlike perhaps your university drive) JAKES PROJECT; (2) for one paper Jake simply included a Sweave document and data files into a compressed archive [@bowers2005dataverse] [SAY ABIT MORE ABOUT WHAT SWEAVE IS IN PRINCIPLE]; (3) for another more computing intensive paper Jake
assembled a set of files that enabled reproduction of our results using the
`make` system [@bowers2008dataverse] [EXPLAIN A BIT MORE OR INCLUDE REF TO WEBSITE?]; (4) Jake also tried the "compendium"
approach [@gentleman2005reproducible,@gentleman2007statistical] which embeds an
academic paper within the R package system [@bowers2011dataverse]; The benefit of the compendium approach is that one is not required to have
access to a command line for `make`: the compendium is downloadable from within
R using `install.packages()` and is viewable using the `vignette()` function in
any operating system than runs R.^[Notice that Jake's reproduction archives and/or
instructions for using them are hosted on the
[Dataverse](http://thedata.org/book/learn-about-project), which is another
system designed to enhance academic collaboration across time and space.]  The
idea that one ought to be able to install and run and use an academic paper
just as one installs and uses statistical software packages is very attractive,
and we anticipate that it will become ever easier to turn papers into R packages
as creative and energetic folks turn their attention to the question of
reproducible research.^[See for example <http://r-pkgs.had.co.nz/>]
Finally, (5) Maarten has been using Dropbox for most of his collaborative projects (https://www.dropbox.com/). ALREADY ABOVE? NOTE BACK

There are some new noteworthy developments also. For example, and similar to R Markdown/KnitR in R Studio, there is Markdoc for STATA users (https://github.com/haghish/MarkDoc). People at UC Berkeley have been developing a is a web app, Jupyter Notebook (http://jupyter.org/), that enables you to make and share documents that include text, code, equations and visualizations in one INCLUDE REF TO GITHUB - USING PYTHON. For researchers working across difference platforms, there is Docker (https://www.docker.com/).
